Expos\'{e} Master Thesis\\ Rollup System for Layer 2 Scaling

### 2022-12-06 meeting-notes/rollup-system/main.tex
some revision are added

Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage of out-of-chain state to L2. By publishing computation results on the chain, they preserve the security of the mainnet. Rollups can process a large number of transactions in a rollup batch and then send only some compressed summary data, defines the changes to be made to the state of the mainnet  to L1. This approach allows fixed costs to be spread across multiple transactions in each batch, thus reducing user charges. Rollups therefore provide a significant improvement in transaction throughput.

@@

For example, the fact that a malicious aggregator can steal funds by publishing invalid transaction and root state. The security of the system relies on an honest verifier re-executing all transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions. Since rollup chain execution is based on the submitted transactions-ralated data, anyone can use this information to execute the rollup state and verify the correctness of the state transitions.
Data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches. To this end, all necessary transaction information must be published in L1 so that the transaction can be re-run if necessary

>>>>

Rollups is an off-chain scaling solution, which reduce computational overhead on the mainnet by moving computations and storage out-of-chain to L2. By publishing computation results on the chain, they preserve the security of the mainnet. Rollups can process a large number of transactions in a rollup batch and then send only some compressed summary data, defines the changes to be made to the state of the mainnet  to L1. This approach allows fixed costs to be spread across multiple transactions in each batch, thus reducing user charges. Rollups therefore provide a significant improvement in transaction throughput.

@@

Due to the fact that a malicious aggregator can steal funds by publishing invalid transaction and root state, the security of the system relies on an honest verifier re-executing transactions in a rollup batch and submitting fraud proofs to challenge invalid state transitions. Since the on-chain execution is based on the submitted transactions-related data, anyone can use this information to execute the rollup state and verify the correctness of the state transitions.
Data availability is critical because without access to the state data, the verifier cannot create fraud evidence to dispute invalid rollup batches. Therefore, all necessary transaction information must be published in L1 so that these transactions can be re-run if necessary.
